---
title: "ChiP-seq peaks will save planet"
author: Hiro Protagonist, Roy Blue, Igor Green, Alice White, John Black
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Abstract
I did some work and the result is:


## Introduction

CHiP-Seq makes peaks. Peaks are good.

```{r peaks}
peaks <- read_tsv("data/TC1-ST2-D0.12_peaks.narrowPeak", 
                  col_names = c("chrom", "chromStart", 
                                "chromEnd", "name", "score", 
                                "strand", "signalValue", 
                                "pValue", "qValue", "peak"))

```

## Methods

Peaks were 

```{r pressure, echo=FALSE}
ggplot(peaks) + geom_histogram( aes(pValue), binwidth= 10)
```

## Results

## Number of peaks on each chromosome
In this example we only have chromosome 12.
```{r}
count(peaks, chrom)
```
## Length of peaks (distribution)

## Min, max of peaks

## Signal Value


### Does the p-value correlate with the signal value?

We have discovered `r nrow(peaks)` peaks.

## Discussion
More research is needed.

## Tasks

1. Switch the output format to Word 
2. Arrange the plots in the e-mail into the main document
3. Describe the statistics of the length of the peaks in a table
4. Discuss the distribution of signal values and p values
5. Include a citation